Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 Discussion.tex
finished edits to section 4.4

\subsection{Special Cases: Discrete Preferences and Known $p$}

@@

\begin{theorem}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has an expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
\end{align*}
and an expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right).  \nonumber
\end{align}
\end{theorem}

@@

\textbf{Case 2: If we know $\MinProb$ in advance.}

If we know $\MinProb$ in advance, we can modify the payment-eligible criteria as follows: Denote $s_0=\min_{s=1,2,\cdots,}\{\frac{1}{\log(s_0)}\leq \frac{\MinProb}{2}\}$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s+s_0)$.
\end{itemize}

The algorithm remains the same as Algorithm~\ref{alg:basic-incentivizing}. Under this new algorithm, we can prove:

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
\end{align*}
\end{theorem}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we define $h(\ell) := 
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$. The rest of the proof remains the same.
\end{proof}

\begin{lemma}  \label{lem:NumP2}
The expected number of time steps in which
Algorithm~\ref{alg:basic-incentivizing}
makes any payment is at most 
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
\end{lemma}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
\end{proof}

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right).  \nonumber
\end{align}
\end{theorem}

\begin{proof}
The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
\begin{itemize}
\item We can use Lemma~\ref{lem:NumP2} to bound the regret when we decide to incentivize;
\item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
\end{itemize}
The rest of the proof remains the same.
\end{proof}

>>>>

\subsection{Tighter Bounds Under Additional Assumptions: Discrete Preferences and Known $p$}

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has an expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
\end{align*}
and an expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right).  \nonumber
\end{align}
\end{theorem}

@@

We now consider an alternate assumption, that $\MinProb$ (or a strictly positive lower bound) is known.
\begin{assumption}
\label{a:known-p}
(Known $\MinProb$) 
A strictly positive lower bound on $\MinProb$ is known in advance.
\end{assumption}
\pfcomment{I wrote the assumption allowing a lower bound, but in the eligibility criterion we just use $\MinProb$.  We can modify the criterion.}

When this assumption holds, we modify Algorithm~\ref{alg:basic-incentivizing} by modifying its payment eligibility criterion as follows.  Let $s_0=\min_{s=1,2,\cdots,}\{\frac{1}{\log(s_0)}\leq \frac{\MinProb}{2}\}$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:
\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s+s_0)$.
\end{itemize}

We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the {\it Known-$\MinProb$ Algorithm.} We prove the following result for this algortithm under Assumption~\ref{a:known-p}.

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-$\MinProb$ Algorithm has an expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
\end{align*}
and an expected regret bounded above by
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right).  \nonumber
\end{align}
\end{theorem}

\begin{proof}
The proof of the expected payment bound follows Lemma~\ref{rst:budget} except we define $h(\ell) := 
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$.

The proof of the expected regret bound first establishes the following upper bound on the number of time steps in which a payment is made:
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
The proof of this result follows that of Lemma~\ref{lem:numP}, except it defines $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.

The proof of the expected regret bound then follows that of Theorem is similar as Theorem~\ref{rst:regret}, except:
\begin{itemize}
\item We use the result above to bound the regret when we incentivize;
\item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
\end{itemize}
\end{proof}
